For the purposes of this performance standard:
\begin{itemize}
	\item \textit{‘Maximum operating level’} = 285 MW.
	\item \textit{‘Minimum operating level’} = -285 MW.
	\item \textit{‘Droop’} means, in relation to frequency response mode, the percentage change in power system frequency as measured at the Connection Point, divided by the percentage change in power transfer of the integrated resource system, expressed as a percentage of the maximum operating level of the integrated resource system.  Droop must be measured at frequencies that are outside the deadband and within the limits of power transfer.
	\item Power system frequency is measured at the Connection Point.
\end{itemize}

\begin{enumerate}[label=(\arabic*)]
	\item an integrated resource system, to the extent it comprises production units, must be capable of operating in frequency response mode such that it automatically provides a proportional:
	\begin{enumerate}[label=(\roman*)]
		\item decrease in power transfer to the power system, with a continuous shift from one to the other mode, in response to a rise in the frequency of the power system as measured at the connection point accompanied by a smooth change in bidirectional unit operating mode between production and consumption; and
		\item increase in power transfer to the power system in response to a fall in the frequency of the power system as measured at the connection point accompanied by a smooth change in bidirectional unit operating mode between production and consumption, 
	\end{enumerate}
	sufficiently rapidly and sustained for a sufficient period for the Integrated Resource Provider (as relevant) to be in a position to offer measurable amounts of all market ancillary services for the provision of power system frequency control.
	\item Nothing in paragraph (2) or (3) requires the integrated resource system to operate below its minimum operating level in response to a rise in power system frequency, or above its maximum operating level in response to a fall in power system frequency.  
	\item The change in power transfer to the power system will occur with no delay beyond that required for stable operation, or inherent in the plant controls, once power system frequency leaves a deadband around 50 Hz.
	\item The integrated resource system’s:
	\begin{enumerate}[label=(\roman*)]
		\item deadband can be set within the range of 0 to ± 1.0 Hz ; and
		\item droop can be set within the range of 2\% to 10\%, droop has been set to 5\%.
	\end{enumerate}
	\item Each control system used to satisfy this performance standard is adequately damped.
	\item The amount of relevant market ancillary service for which the plant is registered will not exceed the amount that would be consistent with this performance standard. 
\end{enumerate}
